Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
Update neurips_2021.tex

  with the choice $\beta \approx 0.576$ and set $A$ and $C$ according to the above with the choice $w \approx 0.288$. These choices are arbitrary and, as we discuss below, the results of this Section were found to hold for a range of choices of $\beta$ and $w$. The orbits that these payoff matrices generate can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which, for each player, lies in the centre of the simplex.

>>>>

  with the choice $\beta \approx 0.576$ and set $A$ and $C$ according to the above with the choice $w \approx 0.288$. These choices are arbitrary and, as we discuss below, the results of this Section were found to hold for a range of choices of $\beta$ and $w$. The resulting orbits can be seen in Figure \ref{fig::convergentShapley}, in which, for each player, they converge to the Nash Equilibrium which lies in the centre of the simplex.
